### 2020-10-07 3_review-responses/V1_review_responses/Reviewer_responses_all.tex

\documentclass{letter}

% To insert commas into large numbers automatically
\usepackage{siunitx}

\begin{document}
\pagenumbering{gobble}

\textbf{Reviewer \#1 Response}

\begin{quotation}
1. Machine learning

While this manuscript contains machine learning in its title, there is no major discussion about it. What is machine learning? How do the authors define it? Is data mining part of machine learning? If so, how so? Why is important or useful to use machine learning particularly for this study? What do the authors want to achieve with machine learning?  
\end{quotation}

Machine learning and data mining often overlap, which is why we had an oversight in defining both of them and explaining their differences. In a journal about Information Technology, we assumed it was general knowledge, but we added it for consistency and for a more widespread reader understanding. In the section previously titled 3.4 "Data mining, knowledge discovery and sentiment analysis", thus renamed 3.4 "Data mining, machine learning, knowledge discovery and sentiment analysis" we introduced two paragraphs defining machine learning, its importance of use for analyzing larger samples, and what we can achieve with it. However the manuscript title changed from another reviewers request.

\begin{quotation}
Also, the manuscript can be improved by justifying and elaborating on the necessity of a large sample. Why is it so important about analysing a large sample? What problem did a "small" sample used in existing literature cause? 
I recommend the authors to prepare a section dedicating to these questions.
\end{quotation}

In regards to the sample size, a paragraph in previously 3.2, now section 3.3 "Chinese and Western tourist behavior" already describes the importance of these bigger samples. We added a bit of text to expand on this importance.

"Although the studies focusing only on Chinese tourists or only on Western tourists have a narrow view, their theoretical contributions are valuable. We can see that depending on the study and the design of questionnaires, as well as the destinations, the results can vary greatly. Not only that, but while there seems to be some overlap in most studies, some factors are completely ignored in one study but not in the other. However, since our study uses data mining, the definition of each subject or factor is left for the hotel customers to decide en masse via their reviews (instead of being defined by the questionnaire). This means that the factors will be selected through statistical methods alone. This opened opportunities to find factors that the writers of this study would not have contemplated, or avoid enforcing a factor on the mind of reviewers by presenting them with a question that they didn't think of by themselves. This large variety of opinions in a big sample, added to the automatic findings of statistical text analysis methods, is what gives an advantage to our study in comparison to others with smaller samples. In addition, this study could help us analyze the satisfaction and dissatisfaction factors cross-culturally and compare them with the existing literature."

\begin{quotation}
2. Theoretical discussion on culture
I also recommend the authors to develop the story on culture with theoretical perspectives. Why would Westerners show different preferences from Chinese? Why do Westerners value soft attributes (or managerial factors) like staff more while Chinese value hard attributes (or environmental factors) like size? Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)? While this study did not measure "culture" per se, I believe the authors can find theoretical explanations.
\end{quotation}

Another reviewer pointed out this, as well as suggesting a new research rationale. Because of it, we added new content to the introduction, changed the abstract and titles, as well as adding a new section in the discussion with theoretical perspectives on the context of Japanese hospitality. It is right that our study did not measure "culture", so we can't be sure of the explanations to certain aspects, although we do explain in the literature review that it has been previously studied how different backgrounds and cultures result in different expectations and as such, different satisfaction factors.

As for the comment "Why do both Westerners and Chinese share dissatisfactory attributes while they show different satisfactory attributes (see Table 6)?": They are both different. RBO results and our hypothesis testing showed that both satisfactory and dissatisfactory attributes are different for both cultures. Still, I understand that explaining the reasoning behind these results could improve the discussion.

\begin{quotation}
3. Restructing
I found the discussion section (7. Discussion) misrepresents. The section is mainly reporting the findings without in-depth discussion (e.g., discussion on the reason behind such findings). I recommend combining Sections 5 and 6 into one section as an analysis section; and rename 7 Discussion as 6 Results. As suggested in the earlier section, the authors can add a new discussion section with a theoretical discussion.
The current 6.1 section can be revised by presenting one-to-one or item-by-item comparison between Chinese and English-speaking customers. The current format is difficult to follow to see which attributes are similar or different between these two groups.
\end{quotation}

We revised the tables in what previously was 6.1 to present them side to side for better following the differences in keyword ranking. They are now tables 5 and 6.

\clearpage
\textbf{Reviewer \#3 Response}

@@

We reconsidered the title from this and another point in this review as follows:

"Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures"

This reflects both points in this comment and focuses on the change in research rationale, while also highlighting the method.

\clearpage
\textbf{Reviewer \#5 Response}

\begin{quotation}
This study used Ctrip as the data base. However, majority users of Ctrip is Mainland Chinese, but Chinese-speaking tourists can also be Taiwanese, Malaysian Chinese, Singaporean Chinese and Hong Konger too. Therefore I suggest the authors change the term Chinese-speaking tourists to Mainland Chinese tourists.
\end{quotation}

Thanks for pointing this information out. We pointed this out in the text.

\begin{quotation}
In literature review, the authors listed three hypothesis relating to Chinese and English speaking tourists in 3.1 and then a separate section 3.2 to explain the difference between Chinese and Western tourists. I would suggest the authors combine these two sections so as to give a more comprehensive view on the setting of the three hypothesis.
\end{quotation}

We respectfully disagree with this suggestion since the content of section 3.1 and 3.2 are very different. While 3.1 sets the premise of differences in customer satisfaction and the reasoning behind them existing, 3.2 discusses previous literature on specific behaviors and cultures of each kind of tourist. Since we added a new section 3.1, these two sections are now 3.2 and 3.3 respectively.

\begin{quotation}
In formular (1), what are alpha, x and y?
\end{quotation}

We added a description of the formula to the manuscript, as well as a short description of the SVM algorithm to make it more understandable.

\begin{quotation}
In the Data Collection, can the authors explain what kinds of hotels (category, Hotel types, or star rating) were extracted? Are the same hotels extracted from both Ctrip and Tripadvisor? How many hotels are there? I believe different types of hotels would have generated different satisfaction level and perspectives. Please provide more details about these hotels.
\end{quotation}

In regards to this point, we apologize and would like to explain. In the original manuscript, the experiments were done while the data was still being collected further. After finishing the manuscript, the original data had changed. Not only this, but we realized our mistake from this and another comment from a different reviewer. Indeed the data should reflect the same kinds of hotels, the same kinds of categories. Since we did not have these data, we decided to match both English and Chinese comments to come from exactly the same hotels, matching by name. This reduced the number of comments on each language, but it made the data fairer. We don't have data on what type of hotel or star rating they had since this data wasn't available to us, but we can be sure they are the same 580 hotels for both kinds of reviews.

\begin{quotation}
In Table 2, I am quite surprise to see that the last item "Chinese person" can be the top keywords with only 16 occurrences. Can the authors explain why there are so few negative Chinese keywords?
\end{quotation}

Since we repeated the experiment, the frequencies have changed, however this keyword still only has 16 occurrences. The lack of negative keywords comes from a peculiarity of the Chinese reviews from Ctrip. Most of the reviews point out the positive extensively, while only a few sentences are negative. It's a limitation of our paper that the negative keywords depend on the sample taken at the beginning, since we could not label more manually at the time.

\begin{quotation}
Regarding the keyword "Big", this is a very general word and can be describe as "Big" in size, "Big in feelings, or could be negative too "big disappointment". Can the authors explain further how this can be avoided in your data analysis?
\end{quotation}

One thing to note is that using SVM, we labeled sentences as positive or negative, so negative usage of the word when counting the frequencies is negligible. In addition to this, we also had the same question when we saw our results the first time, and took a small sample to observe the usage of the word. However we didn't deem it appropriate in the text at first, but with this comment and thinking it over once again, we have added the next paragraph to the manuscript:

>"From these two first ranking keywords (“big” and “clean”), we can assert
that room quality is the most critical satisfaction factor for Chinese customers. However, the word “big” is widespread in the language and could be used in different contexts to point out positive and negative aspects. Since we are interested in how the word is a keyword of positive sentences, we took a small sample of the positively classified sentences that contained the word “big” in Chinese. A team of Chinese speaking lab members then pointed out the usage of the word. Generally speaking, it was used for the spaciousness of rooms, bathtubs, and communal bath facilities."

\begin{quotation}
For the managerial and environmental keywords, what criteria were used for classifying these keywords? 
\end{quotation}

We explain the difference between managerial and environmental factors in different sections of the manuscript. However, since it might still be unclear, we specified the method for classifying the keywords in the Results section, adding the following text:

> "We manually labeled the top
625 keywords of each language into either managerial or environmental by considering how the word would be used when writing a review. If the word implies an issue that could be solved or managed by the hotel staff or management, we consider it managerial. If the word is describing factors that are unchangeable by the staff or management, we consider them environmental. The interpretation of these keywords is shown in the Tables 8 and 9."

We also added the tables that were previously in the appendix clearing this issue into the main text for readability.

\begin{quotation}
Editorial issues
The Appendix is actually part of the manuscript. This manuscript contains too many Tables. First some was mentioned in the manuscript but appeared in Appendix. For example line 306, Table 7 and Section B was mentioned. What is Section B?  Please move all relevant tables to the manuscript but not in Appendix. I would suggest the authors to consider to either combine some of them or not to mention them in the manuscript. 
Besides, the numbering of the tables was not in sequence in the manuscript. Line 360, after Table 3 and 4, it suddenly jumps to Table 10.
\end{quotation}

We moved some tables that we deemed important out of the appendix, but other tables got removed as per this request. We also joined the tables with the top keyword results as per this and another reviewer's request.

### 2020-10-07 3_review-responses/V1_review_responses/olas_review_response.txt

From these two rst ranking keywords (\big" and \clean"), we can assert
that room quality is the most important satisfaction factor for Chinese customers.
This means that Chinese tourists have an expectation of spaciousness
18 E. Aleman Carreon et al.
and cleanliness when coming to Japan, be it by reputation, previous experiences,
or cultural backgrounds.
Ola Jajus

so you went and abandoned the search for discussing it further

kinda like ok so this is happening and the reason is whatever now lets move on
Eli ❤

Oh

Ok I still don’t get where

But you have the same impression then
Ola Jajus
My furry fox girlfriend ❤

had a team of Chinese speaking lab-mates point out the
usage of the word

lab members more professional
Eli ❤

Right
Ola Jajus
My furry fox girlfriend ❤

One key component we found in Chinese customer satisfaction factors is
the inclusion of breakfast within the hotel. This can be inferred from the high
555 frequency with which this keyword was included in the sentences emotionally
classied as positive. While other food-related words were extracted, most of
them were general in nature, like \food" or \eating", and in a lower ranking.
In contrast, the word \breakfast", which is referring to a specic time and
very possibly its inclusion in the hotel commodities, was very frequently used
560 in positive texts compared to other food-related words.
Ola Jajus
My furry fox girlfriend ❤

ok so you explained it all nicely

but you just stopped there without giving further tips to the hotel

i mean ofc the tip is provide free breakfast

but maybe refer to idk some hotel strategy?

if u dont know hotel stuff its hard ik
Eli ❤

Hmmm ok i guess it does come across as withholding information even tho I thought it was obvious
Ola Jajus
My furry fox girlfriend ❤

it is
Eli ❤

Hmm well thanks honey
Ola Jajus
My furry fox girlfriend ❤

ik u probably sum it up later on
Eli ❤

I guess you opened my eyes to why they said that
Ola Jajus
My furry fox girlfriend ❤

yeah maybe u have to translate the results to clear strategies

or end every section of discussion with "Strategies to be implemented: ... include breakfast... ...blah...."
Ola Jajus
My furry fox girlfriend ❤

Moreover, mainland Chinese tourists have expectations about the treatment
towards the Chinese visitors that aren't being met. Be it Chinese language
pamphlets, Chinese texts on instructions for the hotel room and it's
appliances and features (T.V. channels, Wi-Fi setup, etc), or just the treat565
ment towards Chinese people, it seems that their expectations are not being
met. This is natural, since traveling in a strange land without knowledge of
the language can be a daunting experience. Ryan and Mo (2001) also found
that communication diculties was one of the main reasons Chinese customers
would give for not visiting again.
Ola Jajus
My furry fox girlfriend ❤

AGAIN

you got so much to elaborate upon here

even from our experience

ok so they got language bareeer problems SO hotels have to make sure they need to provide a more welcoming environment, hire chinese speaking staff, maybe provide chinese news channels on tv

you could touch on the large no of chinese ryugakusei everywhere in japan and how they could be employed in hotels to increase satisfaction lvls

ik its obvious cuz we both in japan and ryugakusei but even for japanese hotel industry its not crystal clear, and for US ppl its not clear at all

This is all very
Analyzing dierences in satisfaction and dissatisfaction between Chinese and ... 19
dierent from Westerner experiences and while it could be a culture shock to
some, it is mostly seen positively.

this one sounds not professional

"This is all very different" part change to sth like "This lies in striking contrast to" or "This significantly differs with", "This is usually outside the scope of"

also i know you know all this stuff from ur experience but you are not referencing this cultural stuff like sento and bowing and idk is that ok for sure?

"After all, Japanese sta treats all customers
in this respectful manner, but for some customers, this could very well be the
best they have been treated until that moment." this sentence is awkward and too informal

"We can also see that Kozak
585 (2002) and Shanka and Taylor (2004) have also found" also also

you overuse "we can see", change it to sth like "the experimental data suggests", "it can be inferred"

"We can also see that Kozak
585 (2002) and Shanka and Taylor (2004) have also found that hospitality and
sta friendliness is an important determinant in the satisfaction of Western
tourists.
However, we can see"
Eli ❤

ok but the english i told you you can miss because im gonna redo the grammar check
Ola Jajus
My furry fox girlfriend ❤

"we can see from the rest of the keywords" looking at the remaining keywords, we can infer

is gramarly gonna fix informal language or very vague repetitions?

your language is just normal in some places and formal in some; is it gonna detect the discrepancy?

"have found many places unacceptable to their standards" is that an expression for sure? maybe just unacceptable
Ola Jajus
My furry fox girlfriend ❤

"In comparison, our research uncovered that it is mostly linked
to dissatisfaction and that westerners could be said to have high standards of
hygiene when compared to their Chinese counterparts" careful here someone might get offended. maybe use higher standards of room cleanliness; specify its ROOM
Ola Jajus
My furry fox girlfriend ❤

"Some cities in Japan (e.g.
605 Osaka) are currently going under a large number of renovations" ahahah experience
😆
1

"Customers staying in places in renovation
or near a construction" add site

oh man so much english mud

you better fix it all

"Another keyword there is \slow", which upon inspection of example reviews,
610 we concluded that it re
ects the speed of the Internet connection in the hotel
rooms." ORDER screwed up
Eli ❤

order?
Ola Jajus
My furry fox girlfriend ❤

"An interesting detail of the keywords of satisfaction and dissatisfaction,
is that the word \comfortable" is high on the list of satisfaction factors and
\uncomfortable" high on the dissatisfaction factors. It seems that in general,
615 western tourists are highly sensitive to comfort levels in the hotels, and whether
it reaches their expectations." ok so for example what
Eli ❤

ah must be from the new experiment
Ola Jajus
My furry fox girlfriend ❤

thats so curt

it sucks

like comfort of what??? should the hotels invest in beds? balcony sets? big baths?

translate your research to applications
Ola Jajus
My furry fox girlfriend <3 replied to you

order?
no sentence order is shit
Eli ❤

YEAH OK

i told you to leave the english alone jeez

i know it sucks

I'm gonna fix it afterwards
Ola Jajus
My furry fox girlfriend ❤

why didnt you fix it before submitting manuscript?
Eli ❤

because.... that was before i bought grammarly and well apparently it helps a lot

beause apparently my english sucks

now i have it and i plan to use it
👍
1
Ola Jajus
My furry fox girlfriend ❤

"In general, Japan is an expensive place
to visit, which could have an impact in this placement in the ranking." maybe give a frame? like compare a price of room in china and japan in usd?
👍
1

"7.4 Location, location, location" are you sure abt this header?
Eli ❤

well... actually no reviewers complained and it's apparently a phrase used a lot in real estate
👍
1

so its not like... out of nowhere
Ola Jajus
My furry fox girlfriend ❤

"availability of nearby shops" maybe change to proximite to shops

"Upon inspection of examples from the data, we found that most customers
635 were satised if the hotel was nearby to at least two other subjects: subway
or train, and convenience stores." what do you mean by other subjects?

like why other
Eli ❤

oh hmmm... idk really, it can go
Ola Jajus
My furry fox girlfriend ❤

"Japan is a country with a particular public transport system. The rush
hour makes for a subway lled to the brim with people in suits making their
commute, and trains and subway stations in Tokyo create a confusing public
640 transport map for an outside observer. Buses are also available, although less
used than the rail systems in the big cities." particular to peculiar, outside observer to visitor
Ola Jajus
My furry fox girlfriend ❤

"Taxis in Japan
are a luxury compared to other countries. Where in less developed countries
645 the taxi is the cheap method of transport of choice, in Japan, taxis are made
to provide a high-quality experience, with a matching price." ok maybe give a price in usd of train from ueno to tokyo station and taxi so that they get an idea? also if u compare taxi price to usa its comparable so maybe you should add that japanese taxis are expensive compared to other southeast asia countries?
Ola Jajus
My furry fox girlfriend ❤

"This means that
for tourists, subway availability and a good map or plan to travel the city are
of utmost necessity" yo come on dont be out of this century, mention travel apps or google maps or sth

"Japanese convenience stores, on the other hand, are also famous worldwide
650 for their convenience" xDDDDDDD

you dont say

can you rephrase it
Eli ❤

i mean

but they are
😆
1

but yeah sure
Ola Jajus
My furry fox girlfriend ❤

"If some trouble occurred, or a traveler forgot to pack
a certain item, it is almost sure that they can nd it here." hmm i think not,
Ola Jajus
My furry fox girlfriend ❤

"Therefore, considering both transport systems and nearby shops are points
of interest for Chinese and Western tourists, Japanese hotels have to choose
carefully their location from the moment that they are constructed. While not
a top priority, this is a universal factor for both customer groups and it can
be an instant way to generate positive reviews." YES thank you this is what we all wanted
Ola Jajus
My furry fox girlfriend ❤

also more like from the moment they purchase/lease land
👍
1

you could also mention they could purchase land and start buuding after the plans to make new metro line/connection hub are made

like to elaborate a lil on the strategies to take

"After all, even if it doesn't bother some customers, the lack of smell would not
bother any existing customers." i know what ur saying but make it clearer
👍
1

hey im not sure if its a problem but u got "undened 30%" maybe you should comment what that could be and how u could analyze it in future work?
Eli ❤

hmm, well for now it wasnt a problem and i dont wanna angry the reviewer
👍
1
Ola Jajus
My furry fox girlfriend ❤

"However, if hotels want
to attract more and more customers" informal

yeah so u only start to touch on applications a tiny bit in the last part of 7 discussion

basically u need more i think

"Another limitation is that a
big portion of the Asian tourists coming to Japan are Taiwanese and Korean," but istnt chinese veeeery similar to taiwanese

"This
means our hypothesis 2 is rejected (RBOEXT > 0:5), and that the common
ground within both customer groups is also similar in ranking." maybe mention again which one it is

its not like ppl reading the paper gonna remember all ur hypothesis and im always annoyed when i gotta look back
Ola Jajus
My furry fox girlfriend ❤

"Our results and discussion can be utilized as a guideline for managerial
770 decisions when considering Chinese and Western tourists, and we can observe
their stark dierences, as well as their common attributes. In future work...." ok but specify the useful managerial decisions thats like the very worth of this paper
Ola Jajus
My furry fox girlfriend ❤

you worte the paper abt the topic you dont care about

but make it useful for someone who does
Eli ❤

thanks honey
Ola Jajus
My furry fox girlfriend ❤

ok done nice work on future work

ima make dinner im so hungry
❤
1
You replied to My furry fox girlfriend <3

"This
means our hypothesis 2 is rejected (RBOEXT > 0:5), and that the common
ground within both customer groups is also similar in ranking." maybe mention again which one it is
i mean it does say a bit in there but i guess i can add more
Ola Jajus
My furry fox girlfriend ❤

i know, they should remember it after reading the paper but still

for ppl who skim to conclusions...
Eli ❤
